Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-05-31 analysis/paper/shceof.Rmd
Arregla cosas de referencias
Quita lo del monopolo en el abstract

We analyse the joint variabilty of the zonally asymmetric springtime stratospheric and tropospheric circulation using Complex Empirical Orthogonal Functions (cEOF) to characterise planetary waves of varying amplitude and phase. 
The leading cEOF represents variabilty of a zonal wave 1 in the stratosphere and a monopole in the troposphere that correlates slightly with the Symmetric Southern Annular Mode (S-SAM).
The second cEOF (cEOF2) is an alternative representation of the Pacific-South American modes. 
One phase of this cEOF is also extremely correlated with the Asymmetric SAM (A-SAM) in the troposphere. 
Springs with an active ENSO tend to phase-lock the cEOF2, but have no consistent impact on its magnitude.
Furthermore, we find indications that the location of Pacific Sea Surface Temperature anomalies affect the phase of the cEOF2.

@@

In Section\ \@ref(methods) we describe the methods.
In Section\ \@ref(spatial) we analyse the spatial patterns of each complex EOF.
In Section\ \@ref(regressions) we study the spatial regressions with geopotential height, temperature and ozone anomalies.
In Section\ \@ref(psa) and \@ref(sam) we analyse the relationship between cEOF2 the PSA and SAM modes.
In Section\ \@ref(tropical) we study tropical forcings that explain the variability of each cEOF.
In Section\ \@ref(precipitation) we show the relationship between these modes of variability and precipitation and surface temperature anomalies in South America and Oceania.
In Section\ \@ref(discussion) we compare our results with previous studies and discuss the benefits of our methodology.
In Section\ \@ref(conclusion) we summarise the conclusions.

@@

# Discussion and conclusions

>>>>

We analyse the joint variabilty of the zonally asymmetric springtime stratospheric and tropospheric circulation using Complex Empirical Orthogonal Functions (cEOF) to characterise planetary waves of varying amplitude and phase. 
The leading cEOF represents variabilty of a zonal wave 1 troposphere that correlates slightly with the Symmetric Southern Annular Mode (S-SAM).
The second cEOF (cEOF2) is an alternative representation of the Pacific-South American modes. 
One phase of this cEOF is also extremely correlated with the Asymmetric SAM (A-SAM) in the troposphere. 
Springs with an active ENSO tend to phase-lock the cEOF2, but have no consistent impact on its magnitude.
Furthermore, we find indications that the location of Pacific Sea Surface Temperature anomalies affect the phase of the cEOF2.

@@

In Section\ \@ref(methods) we describe the methods.
In Section\ \@ref(spatial) we analyse the spatial patterns of each complex EOF.
In Section\ \@ref(regressions) we study the spatial regressions with geopotential height, temperature and ozone anomalies.
In Section\ \@ref(psa) and \@ref(sam) we analyse the relationship between cEOF2 the PSA and SAM modes.
In Section\ \@ref(tropical) we study tropical forcings that explain the variability of each cEOF.
In Section\ \@ref(precipitation) we show the relationship between these modes of variability and precipitation and surface temperature anomalies in South America and Oceania.
In Section\ \@ref(discussion) we compare our results with previous studies and discuss the benefits of our methodology.

@@

# Discussion and conclusions {#discussion}
